\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-15 doc/paper.tex
give example output for the default CMSSM parameter point

To create a MSSM spectrum generator the following three commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --models=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a MSSM model file.  The \code{configure} scrip checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start MATHEMATICA to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
\begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x
\end{lstlisting}%% $
%
An SLHA input file can be given via the \code{--slha-input-file=}
option, for example:
%
\begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x \
    --slha-input-file=templates/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $

>>>>

To create a MSSM spectrum generator the following three commands:
%
\begin{lstlisting}[language=bash]
$ ./createmodel --models=MSSM
$ ./configure --with-models=MSSM
$ make
\end{lstlisting}%% $
%
The first command creates the model directory \code{models/MSSM/}
together with a MSSM model file.  The \code{configure} scrip checks
the system requirements and creates the \code{Makefile}.  See
\code{./configure --help} for more options.  Executing \code{make}
will start MATHEMATICA to generate the spectrum generator and compile
it.  The resulting executable can be run like this:
\begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x
\end{lstlisting}%% $
%
When executed, the spectrum generator tries to find a set of \DRbar\
model parameters consistent with all CMSSM boundary conditions for the
default parameter point.  Afterwards, the pole mass spectrum and
mixing matrices are calculated and written to the command line in SLHA
format \cite{Skands:2003cj,Allanach:2008qq}.  For the default
parameter point the calculated pole mass spectrum reads
%
\begin{lstlisting}
Block MASS
   1000021     1.15236980E+03   # Glu
   1000024     3.85774164E+02   # Cha_1
   1000037     6.50457634E+02   # Cha_2
        25     1.14751169E+02   # hh_1
        35     7.06790308E+02   # hh_2
        37     7.11386171E+02   # Hpm_2
        36     7.06520770E+02   # Ah_2
   1000012     3.51856408E+02   # Sv_1
   1000014     3.53042587E+02   # Sv_2
   1000016     3.53046535E+02   # Sv_3
   1000022     2.03889708E+02   # Chi_1
   1000023     3.85760548E+02   # Chi_2
   1000025     6.36542302E+02   # Chi_3
   1000035     6.50131337E+02   # Chi_4
   1000001     9.66656167E+02   # Sd_1
   1000003     1.00983192E+03   # Sd_2
   1000005     1.01651888E+03   # Sd_3
   2000001     1.01653020E+03   # Sd_4
   2000003     1.06089549E+03   # Sd_5
   2000005     1.06090253E+03   # Sd_6
   1000011     2.22570345E+02   # Se_1
   1000013     2.29864547E+02   # Se_2
   1000015     2.29888857E+02   # Se_3
   2000011     3.61946702E+02   # Se_4
   2000013     3.61950896E+02   # Se_5
   2000015     3.63136044E+02   # Se_6
   1000002     8.09787908E+02   # Su_1
   1000004     1.01454208E+03   # Su_2
   1000006     1.01981123E+03   # Su_3
   2000002     1.02015283E+03   # Su_4
   2000004     1.05807774E+03   # Su_5
   2000006     1.05808183E+03   # Su_6
\end{lstlisting}
%
To calculate the mass spectrum for a user-defined parameter point, the
CMSSM input parameters can be given in form of a SLHA input file via
the \code{--slha-input-file=} option, for example:
%
\begin{lstlisting}[language=bash]
$ ./models/MSSM/run_MSSM.x \
    --slha-input-file=templates/MSSM/LesHouches.in.MSSM
\end{lstlisting}%% $
